---
title: "Periodicity report"
author: "Andrej-Nikolai Spiess, Stefan Roediger, Michal Burdukiewicz"
date: ""
output:
  html_document:
    toc: true
    theme: united
---

# Periodicity report

Report generated on `r Sys.time()` using [period_app](http://www.smorfland.uni.wroc.pl/shiny/period_app/).

## Data with fitted quadratic model

```{r, echo=FALSE}
plotFit(res.period())
```

Linear model coefficient: `r signif(res.period()[["COEFS"]][1], 3)`.  

Quadratic model coefficient: `r signif(res.period()[["COEFS"]][2], 3)`.  

## Residuals of the model with Loess curve

```{r, echo=FALSE}
plotRes(res.period())
```

Local polynomial regression fit standard error: `r signif(res.period()[["LOESS"]][["s"]], 3)`.

Runs test p-value: `r signif(res.period()[["RUNS"]][["p.value"]], 3)`.  

Ljung-Box test p-value: `r signif(res.period()[["BOX"]][["p.value"]], 3)`.

## Autocorrelation and estimated periodicity

```{r, echo=FALSE}
plotAc(res.period())
```

Estimated periodicity: `r paste(round(mean(res.period()[["PERIOD"]], na.rm = TRUE), 1), "\u00B1", round(sd(res.period()[["PERIOD"]], na.rm = TRUE), 1))`

## Heatmap of position-mapped residuals

```{r, echo=FALSE}
plotHm(res.period())
```

